Characterization and evolution of hourly extreme precipitation in France using an Explicit-Convection Regional Climate Model

### 2025-11-24 article/fig3.qmd
figs
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \input{macros_fig3.tex}
---

@@

\noindent
\begin{minipage}[t]{\paperwidth}
\centering
\setlength{\tabcolsep}{0pt}%
\renewcommand{\arraystretch}{1}%

\begin{tabular}{>{\centering\arraybackslash}p{.24\paperwidth}
                >{\centering\arraybackslash}p{.24\paperwidth}
                >{\centering\arraybackslash}p{.24\paperwidth}
                >{\centering\arraybackslash}p{.24\paperwidth}}
\small\bfseries \shortstack{Number of days\\ per year\\ with precipitation} &
\small\bfseries \shortstack{Annual\\ precipitation\\ total} &
\small\bfseries \shortstack{Mean of daily\\ precipitation\\ maxima} &
\small\bfseries \shortstack{Mean of hourly\\ precipitation\\ maxima} \\[-0.5mm]

@@

\includegraphics[width=\linewidth]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth]{figures/mean-max_pluie_jour.pdf} &
\includegraphics[width=\linewidth]{figures/mean-max_pluie_horaire.pdf} \\[-0.5mm]

\small $ME=\ \meJourPluie\,\mathrm{j}\,(\dJourPluie\%)$ &
\small $ME=\ \meMeanPluieJour\,\mathrm{mm/yr}\,(\dMeanPluieJour\%)$ &
\small $ME=\ \meMeanMaxJour\,\mathrm{mm/day}\,(\dMeanMaxJour\%)$ &
\small $ME=\ \meMeanMaxHoraire\,\mathrm{mm/h}\,(\dMeanMaxHoraire\%)$\\[-0.5mm]

\includegraphics[width=\linewidth]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth]{figures/mean-max_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth]{figures/mean-max_pluie_horaire_diff.pdf}
\end{tabular}

\end{minipage}
\endgroup
```

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \input{macros_fig3.tex}
---

@@

\noindent
\setlength{\tabcolsep}{0pt}%
\renewcommand{\arraystretch}{1}%

\begin{tabular}{>{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}}
\small\bfseries \shortstack{Number of days\\ per year\\ with precipitation} &
\small\bfseries \shortstack{Annual\\ precipitation\\ total} &
\small\bfseries \shortstack{Mean of daily\\ precipitation\\ maxima} &
\small\bfseries \shortstack{Mean of hourly\\ precipitation\\ maxima} \\[-0.5mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_jour.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_horaire.pdf} \\[-0.5mm]

@@

\small $ME=\ \meJourPluie\,\mathrm{d}\,(\mathbf{\dJourPluie}\%)$ &
\small $ME=\ \meMeanPluieJour\,\mathrm{mm/yr}\,(\mathbf{\dMeanPluieJour}\%)$ &
\small $ME=\ \meMeanMaxJour\,\mathrm{mm/day}\,(\mathbf{\dMeanMaxJour}\%)$ &
\small $ME=\ \meMeanMaxHoraire\,\mathrm{mm/h}\,(\mathbf{\dMeanMaxHoraire}\%)$\\[-0.5mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_horaire_diff.pdf}
\end{tabular}

\endgroup
```

### 2025-11-24 article/fig4.qmd
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig5.tex}
---

@@

selected_seasons = ["hydro", "ond", "jfm", "amj", "jas", "avr", "mai", "jui"]
to_plot = combined[combined["season"].isin(selected_seasons)]
plot_r_by_season(to_plot, echelles=['quotidien', 'horaire'], col_values=['numday', 'mean', 'mean-max'], nom_fichier="histo_numday_mean_mean-max")
```

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
---

@@

selected_seasons = ["hydro", "ond", "jfm", "amj", "jas"]
to_plot = combined[combined["season"].isin(selected_seasons)]
plot_r_by_season(to_plot, echelles=['quotidien', 'horaire'], col_values=['numday', 'mean', 'mean-max'], nom_fichier="histo_numday_mean_mean-max")
```

### 2025-11-24 article/fig5.qmd
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig5.tex}
---

@@

trend_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_hydro.svg"
)
trend_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_ond.svg"
)
trend_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jfm.svg"
)
trend_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_amj.svg"
)
trend_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jas.svg"
)
df_trend_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_ond = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_amj = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jas = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

@@

% --- Ligne 3 ---
\textbf{\small YEAR} &
\multirow{3}{*}{
  \begin{minipage}[c]{\linewidth}
    \centering
    \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/quotidien/compare_9/sat_99.0/legend_horiz_signif.pdf}
    \makebox[0.85\linewidth][c]{\small \%}
  \end{minipage}
}\\[-0.5mm]

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig5.tex}
---

@@

trend_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_hydro.svg"
)
trend_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_ond.svg"
)
trend_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jfm.svg"
)
trend_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_amj.svg"
)
trend_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_signif.svg",
  "figures/trend_pluie_jas.svg"
)
df_trend_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_ond = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_amj = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jas = combined_all.loc[(combined_all["echelle"] == "quotidien") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

@@

% --- Ligne 3 ---
\textbf{\small YEAR} &
\multirow{3}{*}{
  \begin{minipage}[c]{\linewidth}
    \centering
    \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/quotidien/compare_5/sat_99.0/legend_horiz_signif.pdf}
    \makebox[0.85\linewidth][c]{\small \%}
  \end{minipage}
}\\[-0.5mm]

### 2025-11-24 article/fig6.qmd
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig6.tex}
---

@@

trend_horaire_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_hydro.svg"
)
trend_horaire_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_ond.svg"
)
trend_horaire_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jfm.svg"
)
trend_horaire_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_amj.svg"
)
trend_horaire_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jas.svg"
)
df_trend_horaire_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_ond = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_amj = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jas = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

@@

    % --- Ligne 3 ---
    \textbf{\small YEAR} &
    \multirow{3}{*}{
      \begin{minipage}[c]{\linewidth}
        \centering
        \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_9/sat_90.0/legend_horiz_signif.pdf}
        \makebox[0.85\linewidth][c]{\small \%}
      \end{minipage}
    }\\[-0.5mm]

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig6.tex}
---

@@

trend_horaire_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/hydro/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/hydro/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_hydro.svg"
)
trend_horaire_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/ond/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/ond/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_ond.svg"
)
trend_horaire_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/jfm/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/jfm/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jfm.svg"
)
trend_horaire_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/amj/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/amj/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_amj.svg"
)
trend_horaire_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/jas/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/jas/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jas.svg"
)
df_trend_horaire_pluie_hydro = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "hydro") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_ond = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "ond") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jfm = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jfm") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_amj = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "amj") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_horaire_pluie_jas = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jas") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

@@

    % --- Ligne 3 ---
    \textbf{\small YEAR} &
    \multirow{3}{*}{
      \begin{minipage}[c]{\linewidth}
        \centering
        \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_5/sat_90.0/legend_horiz_signif.pdf}
        \makebox[0.85\linewidth][c]{\small \%}
      \end{minipage}
    }\\[-0.5mm]
